### 2015-06-22 chapters/ipa_meets_unicode.tex
minor layout update
another minor layout update
update tone handling and reverse arrow code points

As explained in Section~\ref{pitfall-blocks}, the Unicode Standard code space is
subdivided into character blocks, which generally encode characters from a
single script. However, as is illustrated by the IPA, characters that form a
single writing system may be dispersed across several different character
blocks. With its diverse collection of symbols from various scripts and
diacritics, the IPA is spread across 12 blocks in the Unicode
Standard:\footnote{This number of blocks depends on whether only IPA-sanctioned
symbols are counted or if the phonetic symbols commonly found in the literature
are also included, see~\cite[Appendix~C]{Moran2012}. The 157 characters from 12 
code blocks shown here are the characters proposed for ``strict'' IPA encoding, 
as discussed in Section~\ref{ipa-recommendations}.}

\begin{itemize}[itemsep=4pt]
	\item \textsc{Basic Latin }(27 characters) \newline 
	a b c d e f h i j k l m n o p q r s t u v w x y z~.~|
	\item \textsc{Latin-1 Supplement} (4 characters) \newline 
	æ ç ð ø
	\item \textsc{Latin Extended-A} (3 characters) \newline 
	ħ ŋ œ
	\item \textsc{Latin Extended-B} (4 characters) \newline 
	ǀ ǁ ǂ ǃ
	\item \textsc{IPA Extensions} (67 characters) \newline 
	ɐ ɑ ɒ ɓ ɔ ɕ ɖ ɗ ɘ ə ɛ ɜ ɞ ɟ ɠ ɡ ɢ ɣ ɤ ɥ ɦ ɧ ɨ ɪ ɬ ɭ ɮ ɯ ɰ ɱ ɲ ɳ ɴ \newline
	ɵ ɶ ɸ ɹ ɺ ɻ ɽ ɾ ʀ ʁ ʂ ʃ ʄ ʈ ʉ ʊ ʋ ʌ ʍ ʎ ʏ ʐ ʑ ʒ ʔ ʕ ʘ ʙ ʛ ʜ ʝ ʟ ʡ ʢ 
	\item \textsc{Spacing Modifier Letters} (17 characters) \newline
	\dia{02DE} \dia{02E1} \dia{02B7} \dia{02B2} \dia{02E0} \dia{02E4} 
	\dia{02B0} \dia{02BC} \dia{02D0} \dia{02D1} ˥ ˦ ˧ ˨ ˩ {\large ˈ ˌ}
	\item \textsc{Combining Diacritical Marks} (25 characters) \newline 
	\dia{033C} \dia{032A} \dia{033B} \dia{033A} \dia{031F} \dia{0320} \dia{031D} 
	\dia{031E} \dia{0318} \dia{0319} \dia{031C} \dia{0339} \dia{032C} \dia{0325} 
	\dia{0330} \dia{0324} \dia{0329} \dia{032F} \dia{0334} \dia{0303} \dia{0308} 
	\dia{033D} \dia{0306} \dia{031A} \ \dia{0361}◌
	\item \textsc{Greek and Coptic} (3 characters) \newline 
	β θ χ
    \item \textsc{General Punctuation} (2 characters) \newline 
    ‖ \charis{‿}
	\item \textsc{Superscripts and Subscripts} (1 character) \newline
	\dia{207F} 
	\item \textsc{Arrows} (4 characters) \newline 
	↑ ↓ ↗ ↘
	\item \textsc{Latin Extended-C} (1 character): \newline
	\charis{ⱱ}
\end{itemize}

@@

\noindent Finally, Tone markers are put at the end of any such sequence, and the 
tie bar follows at the very end:

\begin{itemize}
  \item[] \textsc{Tone Marks:}
  \begin{itemize}
    \item[→] tone letters <˥ ˦ ˧ ˨ ˩> \textbar{} tone movement <↑ ↓ ↗ ↘>
    \item[→] tie bar <\dia{0361}{\large\fontspec{CharisSIL}◌}>
  \end{itemize}
\end{itemize}

@@

At the end of this chapter we have added a few longish tables summarizing all
159 different unicode codepoints that form the basis of strict-IPA encoding
(107 letters, 45 diacritics and 7 remaining symbols). Each of
these tables shows a typical glyph, and then lists the Unicode Codepoint,
Unicode Name and IPA description for each symbol.

TO DO:
[ordering]
[additions]

@@

  \item \textsc{IPA letters} \newline
        The 107 different IPA letters as allowed in strict-IPA encoding are
        listed in Table~\ref{tab:ipa_letters} starting on
        page~\pageref{tab:ipa_letters}.
  \item \textsc{IPA diacritics} \newline The 45 different IPA diacritics and
        tone markers (both Unicode Modifier Letters and Combining Diacritical
        Marks) as allowed in strict-IPA encoding are listed in
        Table~\ref{tab:ipa_diacritics} starting on
        page~\pageref{tab:ipa_diacritics}.
  \item \textsc{IPA remainders} \newline
        The 7 remaining IPA symbols (boundary and stress markers) as allowed in
        strict-IPA encoding are listed in Table~\ref{tab:ipa_boundaries} on
        page~\pageref{tab:ipa_boundaries}. 
  \item \textsc{IPA additions} \newline
        The 10 proposed additions to the IPA are listed in
        Table~\ref{tab:ipa_additions} on page~\pageref{tab:ipa_additions}.

>>>>

As explained in Section~\ref{pitfall-blocks}, the Unicode Standard code space is
subdivided into character blocks, which generally encode characters from a
single script. However, as is illustrated by the IPA, characters that form a
single writing system may be dispersed across several different character
blocks. With its diverse collection of symbols from various scripts and
diacritics, the IPA is spread across 12 blocks in the Unicode
Standard:\footnote{This number of blocks depends on whether only IPA-sanctioned
symbols are counted or if the phonetic symbols commonly found in the literature
are also included, see~\cite[Appendix~C]{Moran2012}. The 159 characters from 12 
code blocks shown here are the characters proposed for ``strict'' IPA encoding, 
as discussed in Section~\ref{ipa-recommendations}.}

\begin{itemize}[itemsep=4pt]
	\item \textsc{Basic Latin }(27 characters) \newline 
	a b c d e f h i j k l m n o p q r s t u v w x y z~.~|
	\item \textsc{Latin-1 Supplement} (4 characters) \newline 
	æ ç ð ø
	\item \textsc{Latin Extended-A} (3 characters) \newline 
	ħ ŋ œ
	\item \textsc{Latin Extended-B} (4 characters) \newline 
	ǀ ǁ ǂ ǃ
	\item \textsc{Latin Extended-C} (1 character): \newline
	\charis{ⱱ}
	\item \textsc{IPA Extensions} (67 characters) \newline 
	ɐ ɑ ɒ ɓ ɔ ɕ ɖ ɗ ɘ ə ɛ ɜ ɞ ɟ ɠ ɡ ɢ ɣ ɤ ɥ ɦ ɧ ɨ ɪ ɬ ɭ ɮ ɯ ɰ ɱ ɲ ɳ ɴ \newline
	ɵ ɶ ɸ ɹ ɺ ɻ ɽ ɾ ʀ ʁ ʂ ʃ ʄ ʈ ʉ ʊ ʋ ʌ ʍ ʎ ʏ ʐ ʑ ʒ ʔ ʕ ʘ ʙ ʛ ʜ ʝ ʟ ʡ ʢ 
	\item \textsc{Greek and Coptic} (3 characters) \newline 
	β θ χ
	\item \textsc{Spacing Modifier Letters} (17 characters) \newline
	\dia{02DE} \dia{02E1} \dia{02B7} \dia{02B2} \dia{02E0} \dia{02E4} 
	\dia{02B0} \dia{02BC} \dia{02D0} \dia{02D1} ˥ ˦ ˧ ˨ ˩ {\large ˈ ˌ}
	\item \textsc{Superscripts and Subscripts} (1 character) \newline
	\dia{207F} 
	\item \textsc{Combining Diacritical Marks} (25 characters) \newline 
	\dia{033C} \dia{032A} \dia{033B} \dia{033A} \dia{031F} \dia{0320} \dia{031D} 
	\dia{031E} \dia{0318} \dia{0319} \dia{031C} \dia{0339} \dia{032C} \dia{0325} 
	\dia{0330} \dia{0324} \dia{0329} \dia{032F} \dia{0334} \dia{0303} \dia{0308} 
	\dia{033D} \dia{0306} \dia{031A} \ \dia{0361}{\large\fontspec{CharisSIL}◌}
    \item \textsc{General Punctuation} (2 characters) \newline 
    ‖ \charis{‿}
%	\item \textsc{Modifier Tone Letters} (2 characters) \newline
%	{\large\fontspec{CharisSIL}ꜛ ꜜ}
	\item \textsc{Arrows} (4 characters) \newline 
	↑ ↓ ↗ ↘

@@

\noindent Finally, the tie bar follows at the very end of any such sequence:

\begin{itemize}
  \item[] \textsc{Tie bar:}
  \begin{itemize}
%    \item[→] tone letters <˥ ˦ ˧ ˨ ˩>
    \item[→] tie bar <\dia{0361}{\large\fontspec{CharisSIL}◌}>
  \end{itemize}
\end{itemize}

@@

At the end of this chapter we have added a few longish tables summarizing all
159 different unicode codepoints that form the basis of strict-IPA encoding
(107 letters, 36 diacritics and 16 remaining symbols). Each of
these tables shows a typical glyph, and then lists the Unicode Codepoint,
Unicode Name and IPA description for each symbol.

TO DO:
[ordering]
[boundaries, stress, intonation]
[additions]

@@

   \item \textsc{IPA letters} \newline
        The 107 different IPA letters as allowed in strict-IPA encoding are
        listed in Table~\ref{tab:ipa_letters} starting on
        page~\pageref{tab:ipa_letters}.
  \item \textsc{IPA diacritics} \newline The 36 different IPA diacritics and
        tone markers (both Unicode Modifier Letters and Combining Diacritical
        Marks) as allowed in strict-IPA encoding are listed in
        Table~\ref{tab:ipa_diacritics} starting on
        page~\pageref{tab:ipa_diacritics}.
  \item \textsc{IPA remainders} \newline The 16 remaining IPA symbols
        (boundary, stress, tone letters and intonation markers) as allowed in strict-IPA
        encoding are listed in Table~\ref{tab:ipa_leftovers} on
        page~\pageref{tab:ipa_leftovers}. 
  \item \textsc{IPA additions} \newline
        The 10 proposed additions to the IPA are listed in
        Table~\ref{tab:ipa_additions} on page~\pageref{tab:ipa_additions}.

### 2015-06-22 tables/unicode_boundaries.tex
update tone handling and reverse arrow code points

\tablecaption{Strict-IPA boundaries with Unicode encodings}\label{tab:ipa_boundaries}
 \tablefirsthead{
   \toprule
   & Code & Unicode name & IPA name \\ 
   \midrule
   }
 \tablehead{
   \multicolumn{4}{c}{
     \captionsize\tablename\ \thetable{} 
     Strict-IPA boundaries with Unicode encodings --- \textit{continued}
     } \\
   \toprule
   & Code & Unicode name & IPA name \\ 
   \midrule
   }
 \tabletail{
   \bottomrule
   \multicolumn{4}{r}{
     \captionsize\textit{continued on next page}
     } \\
   }
 \tablelasttail{\bottomrule}

\begin{center}
\begin{xtabular}{ l L{1.2cm} L{5.4cm} L{4cm} }
{\large ˈ} & \unif{02C8} & \textsc{modifier letter vertical line} & primary stress \\
{\large ˌ} & \unif{02CC} & \textsc{modifier letter low vertical line} & secondary stress \\
 & \unif{0020} & \textsc{space} & word break \\
{\large.} & \unif{002E} & \textsc{full stop} & syllable break \\
{|} & \unif{007C} & \textsc{vertical line} & minor group break (foot) \\
{‖} & \unif{2016} & \textsc{double vertical line} & major group break (intonation) \\
\charis{‿} & \unif{203F} & \textsc{undertie} & linking (absence of a break) \\
\end{xtabular}
\end{center}

>>>>

\tablecaption{Other Strict-IPA symbols with Unicode encodings}\label{tab:ipa_leftovers}
 \tablefirsthead{
   \toprule
   & Code & Unicode name & IPA name \\ 
   \midrule
   }
 \tablehead{
   \multicolumn{4}{c}{
     \captionsize\tablename\ \thetable{} 
     Other Strict-IPA symbols with Unicode encodings --- \textit{continued}
     } \\
   \toprule
   & Code & Unicode name & IPA name \\ 
   \midrule
   }
 \tabletail{
   \bottomrule
   \multicolumn{4}{r}{
     \captionsize\textit{continued on next page}
     } \\
   }
 \tablelasttail{\bottomrule}

\begin{center}
\begin{xtabular}{ l L{1.2cm} L{5.4cm} L{4cm} }
{\large ˈ} & \unif{02C8} & \textsc{modifier letter vertical line} & primary stress \\
{\large ˌ} & \unif{02CC} & \textsc{modifier letter low vertical line} & secondary stress \\
{˥} & \unif{02E5} & \textsc{modifier letter extra-high tone bar} & extra high tone \\
{˦} & \unif{02E6} & \textsc{modifier letter high tone bar} & high tone \\
{˧} & \unif{02E7} & \textsc{modifier letter mid tone bar} & mid tone \\
{˨} & \unif{02E8} & \textsc{modifier letter low tone bar} & low tone \\
{˩} & \unif{02E9} & \textsc{modifier letter extra-low tone bar} & extra low tone \\
%{\large\fontspec{CharisSIL}ꜛ} & \unif{A71B} & \textsc{modifier letter raised up arrow} & upstep \\
%{\large\fontspec{CharisSIL}ꜜ} & \unif{A71C} & \textsc{modifier letter raised down arrow} & downstep \\
{↑} & \unif{2191} & \textsc{upwards arrow} & global rise \\
{↓} & \unif{2193} & \textsc{downwards arrow} & global fall \\
{↗} & \unif{2197} & \textsc{north east arrow} & global rise \\
{↘} & \unif{2198} & \textsc{south east arrow} & global fall \\
 & \unif{0020} & \textsc{space} & word break \\
{\large.} & \unif{002E} & \textsc{full stop} & syllable break \\
{|} & \unif{007C} & \textsc{vertical line} & minor group break (foot) \\
{‖} & \unif{2016} & \textsc{double vertical line} & major group break (intonation) \\
\charis{‿} & \unif{203F} & \textsc{undertie} & linking (absence of a break) \\
\end{xtabular}
\end{center}
